Improving the Image Acquisition Rate of an Atomic Force Microscope Through Compressive Sampling

### 2019-06-19 latex/afm-cs-main.tex
Update plots; edit documents.

In AFM, implementing a truly random pattern requires that the tip be
engaged with the surface to collect a measurement, lifted and moved to
the new location, and engaged again. Because the re-engagement process
is typically slow, this can lead to excessively long image acquisition
times and negate the gains from undersampling \cite{andersson2012non}.
One discrete undersampling scheme, called a $\mu$-path pattern, was
proposed in \cite{maxwell2014compressed} to improve sampling
efficiency. The $\mu$-path pattern consists of randomly placed short,
horizontal scans (see Fig.~\ref{fig:mu_mask} for one such pattern) and
is designed to balance the randomness needed to ensure good
reconstruction with continuous scanning to reduce the number of tip
engagements. %Though the pattern is motivated from CS, it also works well in practice for inpainting reconstruction \cite{luo2015comparison}.
\todo{Would be beneficial to shrink intro, if possible}

Our previous work on the $\mu$-path pattern using theoretical
calculations, simulations, and a preliminary implementation,
demonstrates that the approach can achieve significant scanning time
reduction while maintaining faithful image reconstruction
\cite{maxwell2014compressed,Luo:2015tu, braker_hardware_2018}. This
paper builds upon that earlier work in several significant ways.

\textbf{Contributions} Much of the prior work on undersampled AFM
images is based purely on simulations \cite{han_optimal_2018,
  Luo_nano_2015, oxvig_structure_2017, jensen_reconstruction_2013,
  maxwell_acc_2014, Chen_2012jx}.

% % ------------------ TKTKTKT ------------------
% \todo{Strike this?} First, we demonstrate performance using both
% randomly-placed $\mu-$paths and designed $\mu-$paths that are
% optimized to minimize the expected reconstruction error given some
% initial estimate of the frequency structure of the sample. These
% schemes are described in Sec. \ref{sec:samplingScheme}.
% % --------------------------
We also introduce a new reconstruction algorithm which is designed to
minimize the artifacts arising from the structure of the $\mu$-path
scanning pattern. This algorithm is described and compared to existing
reconstruction methods through simulations in Sec.
\ref{sec:reconstructionMethods}. Section \ref{sec:control} describes
improvements to the control algorithms compared to our preliminary
implementation in ~\cite{braker_hardware_2018}. We then demonstrate
the entire scheme from sampling through reconstruction using
experiments on a commercial AFM (Agilent 5500). The experimental setup
and implementation details are described in Secs.
\ref{sec:experimentalSetup} and \ref{sec:implementation}\footnote{The
  software portion of the implementation and image reconstruction
  described in this paper can be found at
  \url{https://github.com/rabraker/AFM_CS}}. Experimental results are
provided in Sec. \ref{sec:results}. Finally, we provide a few
concluding remarks in Sec. \ref{sec:conclusions}.

@@

\subsection{Limitations of SSIM and PSNR}\label{sec:limits}
The SSIM and PSNR have become reasonably popular in studies comparing
simulated AFM image reconstructions \cite{oxvig_structure_2017,
  han_optimal_2018, Luo_nano_2015}. However, it remains somewhat of an
open question how to best compare experimental AFM images. While we
use the SSIM and PSNR in Section~\ref{sec:results}, we believe those
numbers should be interpreted with some caution. In our experimental
setup, actuation in the $XY$-plane happens via the nPoint piezo stage
and the $XY$-direction of the original piezo scanner is uncontrolled.
This leads to substantial drift between images. To illustrate this, we
took a sequence of 6 raster scans of a sample grating, each at a 1~Hz
scan rate over a 5 micron by 5 micron area. The top row of
Fig.~\ref{fig:baseline_errors} shows the error between the first and
second image and the first and 6th image. The PSNR and SSIM between
images one and six are \baseline{one2twoNoAlgnPsnr} and
\baseline{one2twoNoAlgnSsim}; between images one and six they are
\baseline{one2sixNoAlgnPsnr} and \baseline{one2sixNoAlgnSsim},
respectively, even though on their own each image has good quality.

To mitigate this affect, we use an image alignment technique based on
the 2D cross-correlation between each image. Essentially, this takes a
sub-slice of image 1 (here, a 25 pixel inset on each edge), and finds
the offset in the other image that produces the smallest error. The
result of this procedure are shown in the bottom row of
Fig.~\ref{fig:baseline_errors}.
% Taking the first scan as the master, we compute the PSNR and SSIM
% metrics. The best PSNR here is 16.57 and the worst is 9.02. The best
% SSIM is 0.54 and the worst is 0.28.
Although the situation is improved compared to the un-aligned images,
there is still noticeable stretching, particularly in the
$Y$-direction. Notably, with the alignment technique, the SSIM is
\baseline{one2twoAlgnSsim} for images one and two, and
\baseline{one2sixAlgnSsim} for images one and six; the PSNR is
\baseline{one2twoAlgnPsnr} and \baseline{one2sixAlgnPsnr}
respectively.

\begin{figure}[t!]
  \centering
  % \includesvg[width=0.7\columnwidth]{figures/baseline_errors_aligned_1Hz.svg}
  \includesvg[width=0.7\columnwidth]{figures/baseline_errors_1and6.svg}
  \caption{Errors between the first and second (left column) and first
    and sixth (right column) raster scans in a sequence of six 1.0~Hz
    raster scans. (top) Errors without alignment (bottom) The same
    data but aligned via cross correlation.}
  \label{fig:baseline_errors}
\end{figure}

\subsection{A new metric}
% \begin{figure}[t!]
%   \centering
%   \includesvg[width=1\columnwidth]{figures/damage_illustration.svg}
%   \caption{The RDI metric defined in \eqref{eqn:RDI} penalizes
%   everything in the red shaded region and does not penalize anything
%   in the un-shaded region.}
%   \label{fig:damage_illustrate}
% \end{figure}

% Th PSNR and SSIM metrics only assess the similarity of two images.
% However, in AFM imaging, pure image quality is not the only concern,
% particularly for delicate samples. What is needed is a figure of
% merit for how much damage was done to specimen during the imaging
% process. While this is not really a concern while imaging a hard
% calibration grating, it plays a prominent role biological
% samples~\cite{ando_highspeed_2008}. In general, damage occurs while
% scanning into an uphill region, which results in a positive
% deflection signal. The actual damage done by a given $Z_d$ will
% depend on the spring constant of the cantilever and the softness of
% the specimen. Nonetheless, we can use the positive deviations of
% $Z_d$ as a relative measure of damage between different scan speeds
% or scanning methods, for a given cantilever and specimen. This
% motivates a metric we term the relative damage index (RDI), which we
% define as
% \begin{align}
%   \text{RDI} &= \frac{1}{T_s}\sum_{k\in I} \frac{1}{k} \left(Z_{d,k} - r_{Z,s}\right)^2 \label{eqn:RDI}\\
%   I &= \{k: k\in[0,~N-1],~ Z_{d,k}-r_{Z,s} > 0 \} \nonumber
% \end{align}
% where $N$ is the total number of samples in a given scan, $Z_{d,k}$
% is the deflection signal at sample $k$ and $r_{Z,\textrm{s}}$ is the
% scanning setpoint. The RDI is basically the power in positive
% deflection. By excluding negative values of the deflection, we do
% not penalize the CS algorithm while it is re-engaging with the
% specimen \emph{unless} it overshoots the scanning setpoint, which we
% do want to penalize. This is illustrated in
% Fig.~\ref{fig:damage_illustrate}, which shows several CS cycles with
% a poorly tuned controller. Only deflection signals in the red-shaded
% region will be penalized by the RDI.

\section{Experimental Results}\label{sec:results}
We compared $\mu$-path scanning to two scenarios. First, we compare it
to full resolution raster scans at several scan rates. Second we
compare to course raster scans.
% For both comparisons, we use the same set of $\mu$-path scans.

\subsection{Comparison to full raster}
We took scans of a Ted Pella CS-20NG sample grating over an area with
holes on a 500 nm pitch. The holes are 20 nm deep. We scanned 5 micron
by 5 micron images using standard raster scans with 512 lines. For the
raster scans, we took scans at 1.0~Hz, 2.5~Hz, 5.0~Hz, 8.0~Hz and
10~Hz. We also took $\mu$-path scans with densities at 12.5\%, 15\%
and 25\% and reconstructed 512 by 512 pixel images. The CS scans we
taken with scan velocities equivalent to raster scan rates of 1.0~Hz,
2.0~Hz, 5.0~Hz and 8.0~Hz. For all CS scans, the $\mu$-paths are
$\scanD{muLenNM}$ nm long, which translates to $\scanD{muLenPix}$
pixels.

The free value of the deflections signal was approximately -0.6 volts
and we set the scanning reference to ${\rzs=\scanD{spScan}}$~volts and
the withdraw reference to ${\rzup=\scanD{spMv}}$ volts. We set the
$XY$-settle boundary to $\pm \scanD{xyBoundaryMic}$ microns and
required $\scanD{xySetSamps}$ samples within this boundary before
moving to the $Z$-engage state. The pre-scan length was
$\scanD{preScanSamples}$ time steps. The cantilever was an Budget
Sensors ContAI-G, with a nominal length of 450 microns and spring
constant of $k=0.2$~N/m.

% \SSData{G2}$& $g_6 = \SSData{G6}
The CS scans were reconstructed with BPVV. We set
${\sigma = \scanD{sigma}}$, ${\mu_f=\scanD{muf}}$,
${\alpha_v=\scanD{alpv}}$ and ${\alpha_h=\scanD{alph}}$. The data
remained scaled in terms of volts.

For the raster scans, we discard data from the re-trace and divided
the remaining data for each scan line into 512 bins based on the \xc
sensor measurements. We then average the data in each bin to obtain
the value of one pixel. To remove the affects of piezo creep and
sample tilt, we then de-trend each individual line. De-trending each
line causes the flat portion between the holes in the horizontal
direction to appear at a different height than the flat portion
between holes in the vertical direction. To remove this effect, we
select a column of pixels on the left and right side of each image
that does not cross any holes (i.e., a vertical line through the flat
area), register each scan line to a common height along these columns.
This step eases comparison with the CS scans and was inspired by a
feature in \texttt{SPIW} \cite{spiw}.

As a final step, we subtract the mean from each CS and raster image,
so that they can all be mapped to the same color intensity in the
images. The color maps represent a range of $\pm$20 nm.

The resulting images are shown in Fig.~\ref{fig:resultsF1_images}. The
rows of pixels indicated by the red lines are shown as cross sections
Fig.~\ref{fig:pixel_rows}.

For each raster scan and each CS scan, we computed the SSIM, PSNR
(both with default parameters) using the 1~Hz scan as the master and
also computed the RDI metric. These are collected in table
~\ref{tab:rast_vs_cs_v1}.

@@

% \begin{table}[t!]
%   \centering
%   \caption{Performance metrics for raster and CS scans.}
%   \begin{tabular}{cccccc}
%     \input{tables/cs_raster_table_4-26-2019_muInf_dct2.tex}
%   \end{tabular}
%   \label{tab:rast_vs_cs_v1}
% \end{table}

@@

\begin{figure}
  \includesvg[width=1\columnwidth]{figures/cs_raster_pixel_rows_6-5-2019.svg}
  \caption{Rows of pixels, as indicated by the red lines in
    Fig.~\ref{fig:resultsF1_images}. For clarity, not all images are
    included.}
  \label{fig:pixel_rows}
\end{figure}

Unfortunately, the SSIM and PSNR metrics are not particularly
illuminating. It is easiest to see this by plotting PSNR and SSIM
against total acquisition time, which is shown in
Fig.~\ref{fig:time_ssim} and ~\ref{fig:time_psnr}. There are several
inconsistencies. First, the 4~Hz raster scan has the lowest PSNR of
all the raster scans, while the 8~Hz scan has the highest. Second, all
of the 15\% CS scans except the 8~Hz version have as good or better
SSIM numbers than the raster scans. It makes no sense for a CS scan at
a 5~Hz rate to have better quality than a raster scan at a 5~Hz rate.

Fig.~\ref{fig:improve_512} shows amount of improvement of the
different sub-sampling techniques over full raster scans with 512
lines as a function of scan rate. As far as pure speed goes, the CS
scan at 12.5\% is the fastest for a rate of 1~Hz, though the 64 line
raster scan is close. At the same time, the image quality of the 1~Hz,
12.5\% CS scan is better than the the 1~Hz 64 line raster scan.
However, this advantage quickly evaporates for faster scan rates.
Indeed, for rates beyond about 5~Hz, the raster scan with 128 lines is
not only faster than the 12.5\% CS scan, it also has (arguably) better
image quality.

Thus, we conclude that $\mu$-path based sub-sampling is only
beneficial when there is an exigent reason to scan slowly. This may be
the case for delicate specimens. We can roughly quantify this by
computing the power in the deflection signal during scanning
\begin{align}
  \text{RDI} &= \frac{1}{T_s}\sum_{k=0}^N \frac{1}{k} \left(Z_{d,k} - r_{Z,s}\right)^2 \label{eqn:RDI}\\
\end{align}
The idea behind the idea is that increased scan rates lead to larger
deflection signals (and thereby increased force into the specimen) at
each surface feature, which the RDI accumulates.

The values of the RDI for each of the $\mu$-path and raster scans are
shown in Fig.~\ref{fig:time_damage} as a function of total imaging
time. As one would expect, as imaging time decreases, the RDI for each
scan type increases.

\begin{figure*}[t!]
  \centering
  \begin{subfigure}{0.329\linewidth}
    \centering
    \includesvg[width=1\columnwidth]{figures/cs_rast_time_vs_ssim.svg}
    \caption{}
    \label{fig:time_ssim}
  \end{subfigure}
  \begin{subfigure}{0.329\linewidth}
    \centering
    \includesvg[width=1\columnwidth]{figures/cs_rast_time_vs_psnr.svg}
    \caption{}
    \label{fig:time_psnr}
  \end{subfigure}
  \begin{subfigure}{0.329\linewidth}
    \centering
    \includesvg[width=1\columnwidth]{figures/cs_rast_damage.svg}
    \caption{}
    \label{fig:time_damage}
  \end{subfigure}
  \caption{Metrics for raster scan at 512, 128 and 64 lines and
    $\mu$-path scans at 12.5\% and 25\% sampling. The scan rate is
    indicated by color while the scan style is indicated by marker
    style. (a) SSIM as a function of total acquisition time. (b) PSNR
    as a function of total acquisition time. (c) RDI as a function of
    total acquisition time.}
  % \label{fig:time_vs_metrics}
\end{figure*}

Where CS seems to really shine is if we look at the RDI for a given
time or scan rate. This is plotted in Fig.~\ref{fig:time_damage}. For
example, the 10~Hz raster scan, which takes about 51 seconds, gives an
RDI of 23.7. All of the CS scans, except for the 15\% scan at 1~Hz
(which is only 0.9 seconds longer) are faster than the 10~Hz raster
scan, yet have much lower RDI values, ranging from 1.21 to 13.13.
Unsurprisingly, the relationship between scan speed and RDI is quite
linear. For the raster scans, the left panel of
Fig.~\ref{fig:time_damage} just plots the inverse relationship of the
right panel, since scan time is inversely proportional to raster
frequency. This is not quite the case for the CS scans due to the
sub-sampling and the fixed overhead which does not scale with scan
rate (e.g., the amount of time for the $XY$-move etc remains
essentially constant for a given scan density).

From the left panel of Fig.~\ref{fig:time_damage}, we see that for a
fixed RDI, CS has a faster imaging acquisition rate. The amount of
improvement is best if we need a very low RDI: for example, if we want
to hold the RDI below 2, then we have to take the 1~Hz raster scan
(512 seconds) while we can achieve the same RDI via CS in about 52
seconds with the 15\% sampling, which is a speed improvement of nearly
10. The higher of an RDI we are willing to tolerate, the advantage of
CS over raster narrows. For example, the 4~Hz raster scan and 5~Hz,
15\% CS scan have comparable RDI, but now CS is only about 6 times
faster. This is a result of the constant overhead imposed by the
engage/disengage and $XY$-move states in CS.

% More importantly though,
\subsection{Comparison to Sub-line Sampling}
Perhaps the simplest alternative to $\mu$-path sampling is to simply
take a standard raster scan with fewer lines. This is the technique we
consider in this subsection. Many of sub-line sampling papers assume
that the lines to sample are selected randomly \cite{han_optimal_2018,
  Luo_nano_2015}. In contrast, we take an even simpler approach scan
every 4th and every 8th line. This yields images with 128 and 64 lines
respectively. For each of these scenarios, we first divide the data
for each line into 512 bins. This gives an image that is 128 (resp.,
64) pixels by 512 pixels. We then linearly interpolate along each
column to produce a 512 by 512 pixel image. Again, we take these
courser raster scans at 1.0, 5.0, 8.0 and 10.0 Hz. The resulting
images are shown in Fig.~\ref{fig:results_subline_images}.

@@

@@

\section{Conclusions}\label{sec:conclusions}
The main conclusion of this chapter is that with CS, it seems that we
can acquire images faster yet (putatively) with less specimen damage
than is possible with raster scanning, which we showed by introducing
a new metric, the RDI. Of course, a natural criticism is that we did
not validate the RDI against delicate specimens. We leave this as an
area for future work.

>>>>

In AFM, implementing a truly random pattern requires that the tip be
engaged with the surface to collect a measurement, lifted and moved to
the new location, and engaged again. Because the re-engagement process
is typically slow, this can lead to excessively long image acquisition
times and negate the gains from undersampling \cite{andersson2012non}.
One discrete undersampling scheme, called a $\mu$-path pattern, was
proposed in \cite{maxwell2014compressed} to improve sampling
efficiency. The $\mu$-path pattern consists of randomly placed short,
horizontal scans (see Fig.~\ref{fig:mu_mask} for one such pattern) and
is designed to balance the randomness needed to ensure good
reconstruction with continuous scanning to reduce the number of tip
engagements.

\textbf{Contributions}
Our previous work on the $\mu$-path pattern using theoretical
calculations, simulations, and a preliminary implementation,
demonstrates that the approach can achieve significant scanning time
reduction while maintaining faithful image reconstruction
\cite{maxwell2014compressed,Luo:2015tu, braker_hardware_2018}. This
paper builds upon that earlier work in several significant ways.

Much of the prior work on undersampled AFM
images is based purely on simulations \cite{han_optimal_2018,
  Luo_nano_2015, oxvig_structure_2017, jensen_reconstruction_2013,
  maxwell_acc_2014, Chen_2012jx} and consequently, there is little discussion of the physical practicality of the proposed methods. For example, most estimates of the potential time savings of sub-sampling techniques are not informed by experiments. Often, a discussion of the harmonic content of the proposed reference signals is typically neglected \cite{luo_continuous_2019, Chen_2012jx,han_optimal_2018}, even though this is a critical concern in AFM. As we show in Section~\ref{sec:control}, the discontinuous nature of the $\mu$-path pattern essentially requires that the control system be to filter the higher frequency content of the step inputs between $\mu$-paths.

Despite this, we show in Section~\ref{sec:results} that $\mu$-path scanning provides a non-trivial speed increase compared to a full quality raster scan. 
% % ------------------ TKTKTKT ------------------
% \todo{Strike this?} First, we demonstrate performance using both
% randomly-placed $\mu-$paths and designed $\mu-$paths that are
% optimized to minimize the expected reconstruction error given some
% initial estimate of the frequency structure of the sample. These
% schemes are described in Sec. \ref{sec:samplingScheme}.
% % --------------------------
We also introduce a new reconstruction algorithm which is designed to
minimize the artifacts arising from the structure of the $\mu$-path
scanning pattern. This algorithm is described and compared to existing
reconstruction methods through simulations in Sec.
\ref{sec:reconstructionMethods}. Section \ref{sec:control} describes
improvements to the control algorithms compared to our preliminary
implementation in ~\cite{braker_hardware_2018}. We then demonstrate
the entire scheme from sampling through reconstruction using
experiments on a commercial AFM (Agilent 5500). The experimental setup
and implementation details are described in Secs.
\ref{sec:experimentalSetup} and \ref{sec:implementation}\footnote{The
  software portion of the implementation and image reconstruction
  described in this paper can be found at
  \url{https://github.com/rabraker/AFM_CS}}. Experimental results are
provided in Sec. \ref{sec:results}. Finally, we provide a few
concluding remarks in Sec. \ref{sec:conclusions}.

@@

\subsection{Limitations of SSIM and PSNR}\label{sec:limits}
The SSIM and PSNR have become reasonably popular in studies comparing
simulated AFM image reconstructions \cite{oxvig_structure_2017,
  han_optimal_2018, Luo_nano_2015}. However, it remains somewhat of an
open question how to best compare experimental AFM images. While we
use the SSIM and PSNR in Section~\ref{sec:results}, we believe those
numbers should be interpreted with some caution. In our experimental
setup, actuation in the $XY$-plane happens via the nPoint piezo stage
and the $XY$-direction of the original piezo scanner is uncontrolled.
This leads to substantial drift between images. To illustrate this, we
took a sequence of 6 raster scans of a sample grating, each at a 1~Hz
scan rate over a 5 micron by 5 micron area. The left image of
Fig.~\ref{fig:baseline_errors} shows the error between the first and
 sixth image. The PSNR and SSIM between
images the first and second images are \baseline{one2twoNoAlgnPsnr} and
\baseline{one2twoNoAlgnSsim}; between the first and sixth are
\baseline{one2sixNoAlgnPsnr} and \baseline{one2sixNoAlgnSsim},
respectively, even though on their own each image has good quality.

To mitigate this affect, we use an image alignment technique based on
the 2D cross-correlation between each image. Essentially, this takes a
sub-slice of image 1 (here, a 25 pixel inset on each edge), and finds
the offset in the other image that produces the smallest error. The
result of this procedure are shown in the right image of
Fig.~\ref{fig:baseline_errors}.
Although the situation is improved compared to the un-aligned images,
there is still noticeable stretching (the upper and lower portions appear considerably worse than the middle). Notably however, with the alignment technique, the SSIM is
\baseline{one2twoAlgnSsim} for both sets of images and
while the PSNR is increases to \baseline{one2twoAlgnPsnr} and \baseline{one2sixAlgnPsnr}
respectively.

\begin{figure}[t!]
  \centering
  % \includesvg[width=0.7\columnwidth]{figures/baseline_errors_aligned_1Hz.svg}
  \includesvg[width=0.7\columnwidth]{figures/baseline_errors_1and6.svg}
  \caption{Errors between the first and sixth raster scans in a sequence of six 1.0~Hz
    raster scans. (left) Errors without alignment (right) The same
    data but aligned via cross correlation.}
  \label{fig:baseline_errors}
\end{figure}

\subsection{A new metric}
Th PSNR and SSIM metrics only assess the similarity of two images.
However, in AFM imaging, pure image quality is not the only concern,
particularly for delicate samples. What is needed is a figure of
merit for how much damage was done to specimen during the imaging
process. While damage to the specimen is not really a concern while imaging a hard
calibration grating, it plays a prominent role for biological
samples~\cite{ando_highspeed_2008}, though damage to the probe itself is still a concern.
In general, the faster the scan rate,
the more difficulty the $Z$-axis control
will have following the sample surface,
which results in a larger $Z_d$ over more time. 
The actual damage done by a given $Z_d$ will
depend on the spring constant of the cantilever and the softness of
the specimen. Nonetheless, we propose a metric, which we call the Relative Damage Index (RDI)
which computes the power in the deflection signal for a given scan. That is,

\begin{align}
  \text{RDI} &= \frac{1}{T_s}\sum_{k=0}^N \frac{1}{k} \left(Z_{d,k} - r_{Z,s}\right)^2 \label{eqn:RDI}\\
\end{align}
The idea behind the RDI is that increased scan rates lead to larger
deflection signals (and thereby increased force into the specimen) at
each surface feature, which the RDI accumulates.

\section{Experimental Results}\label{sec:results}
We compared $\mu$-path scanning to two scenarios. First, we compare it
to full resolution raster scans at several scan rates in Section~\ref{sec:cp_full}.
Second we compare to course raster scans in Section \ref{sec:cp_subline}.

\subsection{Comparison to full raster}\label{sec:cp_full}
We took scans of a Ted Pella CS-20NG sample grating over an area with
holes on a 500 nm pitch. The holes are 20 nm deep. We scanned 5 micron
by 5 micron images using standard raster scans with 512 lines. For the
raster scans, we took scans at 1.0~Hz, 2.5~Hz, 5.0~Hz, 8.0~Hz and
10~Hz. We also took $\mu$-path scans with densities at 12.5\%,
and 25\% and reconstructed 512 by 512 pixel images. The CS scans were
taken with scan velocities equivalent to raster scan rates of 1.0~Hz,
2.0~Hz, 5.0~Hz and 8.0~Hz. For all CS scans, the $\mu$-paths are
$\scanD{muLenNM}$ nm long, which translates to $\scanD{muLenPix}$
pixels.

The free value of the deflections signal was approximately -0.6 volts
and we set the scanning reference to ${\rzs=\scanD{spScan}}$~volts (for both raster and CS)
and the withdraw reference to ${\rzup=\scanD{spMv}}$ volts. We set the
$XY$-settle boundary to $\pm \scanD{xyBoundaryMic}$ microns and
required $\scanD{xySetSamps}$ samples within this boundary before
moving to the $Z$-engage state. The pre-scan length was
$\scanD{preScanSamples}$ time steps. The cantilever was a Budget
Sensors ContAI-G, with a nominal length of 450 microns and spring
constant of $k=0.2$~N/m.

% \SSData{G2}$& $g_6 = \SSData{G6}
The CS scans were reconstructed with BPVV. We set
${\alpha_v=\scanD{alpv}}$ and ${\alpha_h=\scanD{alph}}$. 
For the raster scans, we discard data from the re-trace and divided
the remaining data for each scan line into 512 bins based on the \xc
sensor measurements. We then average the data in each bin to obtain
the value of one pixel. To remove the affects of piezo creep and
sample tilt, we then de-trend each individual line. De-trending each
line causes the flat portion between the holes in the horizontal
direction to appear at a different height than the flat portion
between holes in the vertical direction. To remove this effect, we
select a column of pixels on the left and right side of each image
that does not cross any holes (i.e., a vertical line through the flat
area), register each scan line to a common height along these columns.
This step eases comparison with the CS scans and was inspired by a
feature in the AFM image processing toolbox \texttt{SPIW} \cite{spiw}.
The resulting images are shown in Fig.~\ref{fig:resultsF1_images}.
The color maps represent a range of $\pm$20 nm. The
rows of pixels indicated by the red lines are shown as cross sections
Fig.~\ref{fig:pixel_rows}.

@@

% \begin{table}[t!]
%   \centering
%   \caption{Performance metrics for raster and CS scans.}
%   \begin{tabular}{cccccc}
%     \input{tables/cs_raster_table_6-5-2019_muInf_dct2.tex}
%   \end{tabular}
%   \label{tab:rast_vs_cs_v1}
% \end{table}

@@

\begin{figure}
  \includesvg[width=1\columnwidth]{figures/cs_raster_pixel_rows_6-5-2019.svg}
  \caption{Rows of pixels, as indicated by the red lines in
    Fig.~\ref{fig:resultsF1_images}. For clarity, not all images are
    included.}
  \label{fig:pixel_rows}
\end{figure}
For each raster scan and each CS scan, we computed the SSIM and PSNR
 using the 1~Hz scan as the master and
also computed the RDI metric. These are plotted against total acquisition time
in Fig.~\ref{fig:time_ssim} and ~\ref{fig:time_psnr}.
Unfortunately, the SSIM and PSNR metrics are not particularly
illuminating. There are several inconsistencies. For example, it makes no sense
the 1 Hz CS scan at 25\% has a \emph{worse} PSNR and SSIM than 5 Hz version;
nor does it make sense that the 8~Hz full raster scan has a worse SSIM and PSNR than
the 10~Hz full raster scan.

\begin{figure*}[t!]
  \centering
  \begin{subfigure}{0.329\linewidth}
    \centering
    \includesvg[width=1\columnwidth]{figures/cs_rast_time_vs_ssim.svg}
    \caption{}
    \label{fig:time_ssim}
  \end{subfigure}
  \begin{subfigure}{0.329\linewidth}
    \centering
    \includesvg[width=1\columnwidth]{figures/cs_rast_time_vs_psnr.svg}
    \caption{}
    \label{fig:time_psnr}
  \end{subfigure}
  \begin{subfigure}{0.329\linewidth}
    \centering
    \includesvg[width=1\columnwidth]{figures/cs_rast_damage.svg}
    \caption{}
    \label{fig:time_damage}
  \end{subfigure}
  \caption{Metrics for raster scan at 512, 128 and 64 lines and
    $\mu$-path scans at 12.5\% and 25\% sampling. The scan rate is
    indicated by color while the scan style is indicated by marker
    style. (a) SSIM as a function of total acquisition time. (b) PSNR
    as a function of total acquisition time. (c) RDI as a function of
    total acquisition time.}
  \label{fig:time_vs_metrics}
\end{figure*}

Things are clearer if we plot the RDI for each scan against total acquisition time, which is
shown inf Fig.~\ref{fig:time_damage} and 
this is where CS seems to shine.
This is plotted in Fig.~\ref{fig:time_damage}.
As one would expect, as imaging time decreases, the RDI for each
scan type increases. 
From Fig.~\ref{fig:time_damage}, we see that for a
fixed RDI, CS has a faster imaging acquisition rate. The amount of
improvement is best if we need a very low RDI: for example, if we want
to hold the RDI below 2, then we have to take the 1~Hz raster scan
(512 seconds) while we can achieve the same RDI via CS in about 52
seconds with the 15\% sampling, which is a speed improvement of nearly
10. The higher of an RDI we are willing to tolerate, the advantage of
CS over raster narrows. For example, the 4~Hz raster scan and 5~Hz,
15\% CS scan have comparable RDI, but now CS is only about 6 times
faster. This is a result of the constant overhead imposed by the
engage/disengage and $XY$-move states in CS.

\subsection{Comparison to Sub-line Sampling} \label{sec:cp_subline}
 Many of sub-line sampling papers assume
that the lines to sample are selected randomly \cite{han_optimal_2018,
  Luo_nano_2015}. An even simpler alternative to
$\mu$-path sampling is to simply 
take a standard raster scan with fewer lines. This is the technique we
consider in this subsection, by scanning images with 
 128 and 64 lines. For each of these scenarios, we first divide the data
for each line into 512 bins. This gives an image that is 128 (resp.,
64) pixels by 512 pixels. We then linearly interpolate along each
column to produce a 512 by 512 pixel image. Again, we take these
courser raster scans at 1.0, 5.0, 8.0 and 10.0 Hz. The resulting
images are shown in Fig.~\ref{fig:results_subline_images}.

@@

Fig.~\ref{fig:improve_512} shows the amount of improvement of the
different sub-sampling techniques over full raster scans with 512
lines as a function of scan rate. As far as pure speed goes, the CS
scan at 12.5\% is the fastest for a rate of 1~Hz, though the 64 line
raster scan is close. At the same time, the image quality of the 1~Hz,
12.5\% CS scan is better than the the 1~Hz 64 line raster scan.
However, this advantage quickly evaporates for faster scan rates.
Indeed, for rates beyond about 5~Hz, the raster scan with 128 lines is
not only faster than the 12.5\% CS scan, it also has (arguably) better
image quality.

@@

\section{Conclusions}\label{sec:conclusions}
The main conclusion of this chapter is that with CS, it seems that we
can acquire images faster yet (putatively) with less specimen damage
than is possible while raster scanning a full image. On the other hand, it appears that reconstructing a course raster scan makes more sense for faster scan rates. This is notable, since a course raster scan only requires an additional step in post-processing. It remains to be seen if this conclusion holds for a wide range of instruments.
